### 2019-10-30 Paper_shortened_pdf.Rmd
Create figure 1, fix tables

To address our research questions, we used multilevel, autoregressive structural equation modeling [@asparouhovDynamicStructuralEquation2018]. In this approach, the variance in qualitative parenting behaviors and emotional adjustment is partialized into stable between-individual differences (the mean level for that individual across all measurement occasions), and within-individual fluctuations (deviations from this person-specific mean). This has several advantages: First, controlling for stable between-family differences allows us to estimate the direction of within-family effects more accurately [@hamakerCritiqueCrosslaggedPanel2015]. Any stable factors which might bias cross-lagged effects - such as the influence of SES or neighborhood effects - are accounted for at the between level, and reflected in the correlations between the random intercepts. Secondly, this approach enables us to directly test our hypothesis that between-family differences in quantitative involvement moderate the interplay between qualitative involvement and emotional adjustment: Between-family differences in the interplay between qualitative parenting behaviors and emotional adjustment are estimated as random effects, and we can include between-family level moderators as predictors of these random effects. In this way, we included total joint childcare, the childcare distribution, and child sex as moderators. We conducted separate analyses for the four qualitative parenting dimensions, because a model including all four variables at once was too complex to estimate.

@@

```{r tabinvolvement, results = "asis"}
tabinv <- tab_std_sections$`Effects of quantitative involvement on parenting and adjustment`[c(1:4, 1, 5:7),]
tabinv$Parameter[c(1,5)] <- c("Effects of joint quantitative involvement on random intercepts of:",
                              "Effects of relative quantitative involvement on random intercepts of:")
tabinv$Parameter <- gsub("^(.+) on.*$", "\\1", tabinv$Parameter)
#reg_table(tabinv, caption = "Effects of quantitative involvement on parenting and adjustment", note = "Emo.: Emotional adjustment. *: <5% of posterior has opposite sign from estimate.")
tabinvmod <- rbind(
  tab_std_sections$`Moderating effect of quantitative involvement on parenting effects`[c(1:3, 1, 4:5),],
  tab_std_sections$`Moderating effect of quantitative involvement on child effects`[c(1:3, 1, 4:5),])
tabinvmod$Parameter <- gsub("^.+?(Mother|Father).+?$", "\\1", tabinvmod$Parameter)
tabinvmod$Parameter[c(1,4,7,10)] <- c("Moderating effects of joint involvement on parenting effects of:",
                              "Moderating effects of relative involvement on parenting effects of:",
                              "Moderating effects of joint involvement on child effects on:",
                              "Moderating effects of relative involvement on child effects on:")
tab <- rbind(tabinv, tabinvmod)
#tab[is.na(tab)] <- ""
rownames(tab) <- NULL
reg_table(tab, caption = "Effects of quantitative involvement", note = "Emo.: Emotional adjustment. *: <5% of posterior has opposite sign from estimate.")
```

>>>>

To address our research questions, we used multilevel, autoregressive structural equation modeling [@asparouhovDynamicStructuralEquation2018]. In this approach, the variance in qualitative parenting behaviors and emotional adjustment is partialized into stable between-individual differences (the mean level for that individual across all measurement occasions), and within-individual fluctuations (deviations from this person-specific mean). This has several advantages: First, controlling for stable between-family differences allows us to estimate the direction of within-family effects more accurately [@hamakerCritiqueCrosslaggedPanel2015]. Any stable factors which might bias cross-lagged effects - such as the influence of SES or neighborhood effects - are accounted for at the between level, and reflected in the correlations between the random intercepts. Secondly, this approach enables us to directly test our hypothesis that between-family differences in quantitative involvement moderate the interplay between qualitative involvement and emotional adjustment: Between-family differences in the interplay between qualitative parenting behaviors and emotional adjustment are estimated as random effects, and we can include between-family level moderators as predictors of these random effects. In this way, we included total joint childcare, the childcare distribution, and child sex as moderators. Figure \@ref(fig:figure1) shows a graphical representation of the resulting model. We conducted separate analyses for the four qualitative parenting dimensions, because a model including all four variables at once was too complex to estimate.

```{r figure1, out.width="100%", fig.cap="Abbreviations: `T-1' (the previous measurement occasion), `ri' (random intercept), `s' random slope, `M' (Mother's qualitative involvement), `E' (Emotional adjustment), `F' (Father's qualitative involvement), `inv' (quantitative involvement). Thus, `sME' represents the random slope of Mothers' qualitative involvement on emotional adjustment."}
knitr::include_graphics("Figure1.png")
```

@@

```{r tabinvolvement, results = "asis"}
tabinv <- tab_std_sections$`Effects of quantitative involvement on parenting and adjustment`[c(1:4, 1, 5:7),]
tabinv$Parameter[c(1,5)] <- c("Effects of joint quantitative involvement on random intercepts of:",
                              "Effects of relative quantitative involvement on random intercepts of:")
tabinv$Parameter <- gsub("^(.+) on.*$", "\\1", tabinv$Parameter)
#reg_table(tabinv, caption = "Effects of quantitative involvement on parenting and adjustment", note = "Emo.: Emotional adjustment. *: <5% of posterior has opposite sign from estimate.")
tabinvmod <- rbind(
  tab_std_sections$`Moderating effect of quantitative involvement on parenting effects`[c(1:3, 1, 4:5),],
  tab_std_sections$`Moderating effect of quantitative involvement on child effects`[c(1:3, 1, 4:5),])
tabinvmod$Parameter <- gsub("^.+?(Mother|Father).+?$", "\\1", tabinvmod$Parameter)
tabinvmod$Parameter[c(1,4,7,10)] <- c("Moderating effects of joint involvement on parenting effects of:",
                              "Moderating effects of relative involvement on parenting effects of:",
                              "Moderating effects of joint involvement on child effects on:",
                              "Moderating effects of relative involvement on child effects on:")
tab <- rbind(tabinv, tabinvmod)
#tab[is.na(tab)] <- ""
rownames(tab) <- NULL
cat(as.character(reg_table(tab, caption = "Effects of quantitative involvement", note = "Emo.: Emotional adjustment. *: <5% of posterior has opposite sign from estimate.")))
```
